The CrypTool Script: \\ Cryptography, Mathematics and more \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free eLearning program CrypTool\\ (9th edition -- distributed with CrypTool version 1.4.20)} \vspace{60pt}

### 2009-06-30 script/en/chapters/paper_and_pencil.tex
Use the book class for the script, instead of the article class

@@

\section{Paper and Pencil Encryption Methods}
\label{Kapitel_PaperandPencil}
(Christine St\"otzel, April 2004; Updates: B.+C. Esslinger, June 2005)
\index{Paper- and pencil methods}

@@

\vskip +20 pt
%------------------------------------------------------------------------------
\subsection{Transposition ciphers}

@@

%------------------------------------------------------------------------------
\subsubsection{Introductionary samples of different transposition ciphers}
\label{introsamplesTranspositionCiphers}

@@

%------------------------------------------------------------------------------
% {\bf Column and row transposition}
\newpage % Damit die Tables immer direkt nach dem zugehörigen Item. 
\subsubsection[Column and row transposition ciphers]
    {Column and row transposition\footnotemark}
    \footnotetext{%
Most of the following methods can be simulated in CrypTool\index{CrypTool} 
under the menu {\bf Crypt/Decrypt \textbackslash{} Symmetric (classic) 
\textbackslash{} Permutation}.}

@@

%------------------------------------------------------------------------------
\subsubsection{Further transposition algorithm ciphers}

@@

%------------------------------------------------------------------------------
\newpage % Damit die Tables immer direkt nach dem zugehörigen Item. 
\subsection{Substitution ciphers}
\index{Substitution}

%------------------------------------------------------------------------------
\subsubsection{Monoalphabetic substitution ciphers}
Monoalphabetic substitution\index{Substitution!monoalphabetic} assigns one 
character of the ciphertext alphabet to each plaintext character. This mapping
remains unchanged during the whole process of encryption.
\label{monoalphabeticSubstitutionCiphers}

@@

\newpage % Damit die Tables immer direkt nach dem zugehörigen Item. 
%------------------------------------------------------------------------------
\subsubsection{Homophonic substitution ciphers}

@@

%------------------------------------------------------------------------------
\subsubsection{Polygraphic substitution ciphers}
\label{polygraphicSubstitutionCiphers}

@@

%------------------------------------------------------------------------------
\subsubsection{Polyalphabetic substitution ciphers}

@@

%------------------------------------------------------------------------------
\subsection{Combining substitution and transposition}

@@

\newpage % Damit die Tables immer direkt nach dem zugehörigen Item. 
%------------------------------------------------------------------------------
\subsection{Further methods}
\label{Further-PaP-methods}

>>>>

\chapter{Paper and Pencil Encryption Methods}
\label{Kapitel_PaperandPencil}
(Christine St\"otzel, April 2004; Updates: B.+C. Esslinger, June 2005)
\index{Paper- and pencil methods}

@@

@@

\vskip +20 pt
%------------------------------------------------------------------------------
\section{Transposition ciphers}

@@

%------------------------------------------------------------------------------
\subsection{Introductionary samples of different transposition ciphers}
\label{introsamplesTranspositionCiphers}

@@

%------------------------------------------------------------------------------
% {\bf Column and row transposition}
\newpage % Damit die Tables immer direkt nach dem zugehörigen Item. 
\subsection[Column and row transposition ciphers]
    {Column and row transposition\footnotemark}
    \footnotetext{%
Most of the following methods can be simulated in CrypTool\index{CrypTool} 
under the menu {\bf Crypt/Decrypt \textbackslash{} Symmetric (classic) 
\textbackslash{} Permutation}.}

@@

%------------------------------------------------------------------------------
\subsection{Further transposition algorithm ciphers}

@@

%------------------------------------------------------------------------------
\newpage % Damit die Tables immer direkt nach dem zugehörigen Item. 
\section{Substitution ciphers}
\index{Substitution}

%------------------------------------------------------------------------------
\subsection{Monoalphabetic substitution ciphers}
Monoalphabetic substitution\index{Substitution!monoalphabetic} assigns one 
character of the ciphertext alphabet to each plaintext character. This mapping
remains unchanged during the whole process of encryption.
\label{monoalphabeticSubstitutionCiphers}

@@

\newpage % Damit die Tables immer direkt nach dem zugehörigen Item. 
%------------------------------------------------------------------------------
\subsection{Homophonic substitution ciphers}

@@

%------------------------------------------------------------------------------
\subsection{Polygraphic substitution ciphers}
\label{polygraphicSubstitutionCiphers}

@@

%------------------------------------------------------------------------------
\subsection{Polyalphabetic substitution ciphers}

@@

%------------------------------------------------------------------------------
\section{Combining substitution and transposition}

@@

\newpage % Damit die Tables immer direkt nach dem zugehörigen Item. 
%------------------------------------------------------------------------------
\section{Further methods}
\label{Further-PaP-methods}
